IMF and Benchmark Forecasts

### 2023-09-07 manuscript/manuscript.Rmd
current analysis

>>>>

#############block to merge with cvgdat symmetric

cvgdat_cpin <- data.table::fread(here("quantile_forecasts", "cvg_pooled_directionalsymmetric.csv")) |>
  setnames("model", "source") |>
  .d(, c( "target", "error_method", "method", "source", cols), with = FALSE) |>
  melt(id.vars = c("target", "error_method", "method", "source"),
       variable.name = "pilvl",
       value.name = "coverage") |>
  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
  .d(, pilvl := as.numeric(pilvl)/100) |>
  .d(target == "pcpi_pch") |>
  rbind(cvgdat_cpi)

cvgdat_cpi <- cvgdat_cpin

cvgdat_gdpn <- data.table::fread(here("quantile_forecasts", "cvg_pooled_directionalsymmetric.csv")) |>
  setnames("model", "source") |>
  .d(, c( "target", "error_method", "method", "source", cols), with = FALSE) |>
  melt(id.vars = c("target", "error_method", "method", "source"),
       variable.name = "pilvl",
       value.name = "coverage") |>
  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
  .d(, pilvl := as.numeric(pilvl)/100) |>
  .d(target == "ngdp_rpch") |>
  rbind(cvgdat_gdp)

cvgdat_gdp <- cvgdat_gdpn
